$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-04 paper/paper.tex
Notes on Allais and Thiemann

\subsection{Notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h]
  \begin{mathpar}
    \datatype
    { }
    {\type{\N} : \Set}
    \; \textsc{Nat}

@@

    \inferrule
    {n : \type{\N}}
    {\suc n : \type{\N}}
  \end{mathpar}
  \caption{Notation used in this paper}
\end{figure}

Data type definitions use double lines and index-free synonyms as rule names (for ease of reference).
We otherwise use the constructor name as the name of a typing rule.
Universe levels and universe polymorphism are omitted for brevity --- all our types are of type $\Set$.
Implicit arguments are mentioned by type definitions but omitted in constructors.
$\type{TYPES}$ are blue volet (uppercased, with indices as subscripts), $\constr{constructors}$ are burnt orange, $\func{functions}$ are olive green, variables are black, and some constructor names are overloaded --- and disambiguated by context.

@@

This work is heavily based on the work by Allais \cite{Allais2018a}.
Allais uses leftover typing to build a bidirectional type system for the linear \lambdacalc{}.
He proves type preservation and provides a procedure that decides type checking and type inference.
He then goes on showing the soundness and completeness with respect to the sequent calculus for intuitionistic linear logic.

\cite{Thiemann2019}
\cite{Rouvoet2020}
\cite{Veltri2020}

>>>>

\subsection{Notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The notation used in this paper is given in \autoref{fig:notation}.
\begin{figure}[h]
  \begin{mathpar}
    \datatype
    { }
    {\type{\N} : \Set}
    \; \textsc{Nat}

@@

    \inferrule
    {n : \type{\N}}
    {\suc n : \type{\N}}
  \end{mathpar}
  \caption{Notation used in this paper}
  \label{fig:notation}
\end{figure}

Data type definitions use double lines and index-free synonyms as rule names (for ease of reference).
For example ... \todo{complete the dots here, explain the rules above, in particular the 1+}
We otherwise use the constructor name as the name of a typing rule. For example,...
Universe levels and universe polymorphism are omitted for brevity --- all our types are of type $\Set$. This means that ...
Implicit arguments are mentioned by type definitions but omitted in constructors.

We use colours to further distinguish the different entities in this paper.
$\type{TYPES}$ are blue violet (uppercased, with indices as subscripts), $\constr{constructors}$ are burnt orange, $\func{functions}$ are olive green, variables are black, and some constructor names are overloaded --- and disambiguated by context.

@@

Most of the work on mechanising resource-aware calculi is very recent.

This work is heavily based on the work by Allais \cite{Allais2018a}.
Allais uses leftover typing to build a bidirectional type system for the linear \lambdacalc{}.
He proves type preservation and provides a decision procedure for type checking and type inference.
He then goes on showing the soundness and completeness with respect to the sequent calculus for intuitionistic linear logic.
Also extrinsic.
Also in Agda.
Also de Bruijn.
We apply this to the \picalc{}.
We generalise the usage algebra.
Our type system is not bidirectional --- scope restriction needs usage annotations.
Adding bidirectionality would provide us with a decision procedure for type checking.

\cite{Thiemann2019}
intrinsicly typed
linear session types with recursion and subtyping.
also in Agda.
Also de Bruijn.
semantics as an intrinsically typed CEK machine
explicit context splits
MicroSession, minimal GV, lambda calculus with session types
contexts remove elements with multiplicity 0
keeps a global session context

\cite{Goto2016a}
first session-type paper with a mechanised proof of type safety
Session types
Coq
Extrinisically typed
Session type polymorphism

\cite{Rouvoet2020}
\cite{Veltri2020}
\cite{Gay2001}
